---
title: "Dwell Time Analysis"
author: "redminers"
date: "November 15, 2015"
output: html_document
---

This R Analysis, loads the data directly from the tables at MySQL server hosted at UITS, IU.

Creating an connection, Lets check the average dwell time per stop across all routes,
```{R}
library(RMySQL)
library(ggplot2)
mydb = dbConnect(MySQL(), user='bususer', password='Password123', dbname='iubus', host='rdc04.uits.iu.edu',port=3099)
rs = dbSendQuery(mydb, "select from_stp,avg(dwell_time) 'dwell_time' from route_run_temp where dwell_time <> 0 group by from_stp order by dwell_time")
data = fetch(rs, n=-1)
ggplot(data,aes(x=from_stp,y=dwell_time,color=from_stp,fill=from_stp))+stat_summary(fun.y="mean",geom="bar")+theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.position="none")

```

It can be seen that except the Stadiums, all other stops have about nearly same dwell time except few 'popular' stops.

Lets dig in a little Deep, lets see dwell time across routes,
```{r}
rs = dbSendQuery(mydb, "select from_stp,avg(dwell_time) 'dwell_time',route_id from route_run_temp where dwell_time <> 0 group by from_stp,route_id order by route_id")
data = fetch(rs, n=-1)
ggplot(data,aes(x=from_stp,y=dwell_time,color=from_stp,fill=from_stp))+ylim(0,100)+facet_grid(route_id~.)+stat_summary(fun.y="mean",geom="bar")+theme(axis.text.x = element_text(angle = 90, hjust = 1),legend.position="none")
```

Here the stadium stops are omitted. This graph gives different insight.
It can be seen that the popular stops like IMU spikes up in all routes.

Now lets see the Travel time between the stops for different routes,
Assuming the directionality is specified as column titles.

```{r, echo=FALSE}
rs = dbSendQuery(mydb, "select from_stp,to_stp,avg(travel_time) 'travel_time',route_id from route_run_temp where travel_time <> 0 group by from_stp,route_id order by route_id")
data = fetch(rs, n=-1)
print(data)
```

First impression is that there are few junk values. There are stops which have high travelling time like 7 days, which is not possible. There are few acceptable valid values like IMU and Informatics takes about 2 minutes, which is true in real case also.
